Reaction-diffusion spatial modeling of COVID-19 in Chicago

### 2021-07-20 draft/chicago-spatial-covid-draft.tex
Update chicago-spatial-covid-draft.tex

@@

>>>>

\section{Introduction and Similar Work}

@@

Since the transition rate $\gamma$ is an ``individual'' parameter, and thus acts ``on average'', we preserve the same value at the PDE level as at the ODE level.
The transmission rate $\beta$ is more complicated, since at the PDE level the quantities $S$, $I$, and $R$ are densities rather than populations,
which integrate over the spatial surface to the true population of each category.
